Safe Transferable Regions

### 2016-01-31 paper/related.tex
Related work with Cyclone added.

Cyclone~\cite{cyclone02} equips C with programmer-managed stack
regions, and a typing discipline that statically guarantees the safety
of all pointer dereferences. However, types need to be written
explicitly. While some region annotations can be inferred, type
inference is purely intraprocedural, and cannot infer region types for
functions. Later proposal~\cite{cyclone04} extends Cyclone with
dynamic regions, imposes unique pointer restrictions to guarantee
safety. Objects that need to be shared within data structures are
allowed to have multiple references, and safety for such objects was
ensured via runtime reference counting.

>>>>

Cyclone~\cite{cyclone02} equips C with programmer-managed stack
regions, and a typing discipline that statically guarantees the safety
of all pointer dereferences. Later
proposals~\cite{cyclone04,cycloneSCP} extends Cyclone with dynamic
regions. \name differs from Cyclone fundamentally because of its
non-intrusiveness design principle, which requires its safety
mechanisms to not intrude on the the programming practices of C\#.
\name programmers, for example, shouldn’t be forced to abandon
iterators in favor of for-loops, annotate region types, or rewrite
C\#'s standard libraries to use in \name.  Non-intrusiveness is not a
design consideration for Cyclone, which requires C programmers to use
new language constructs and abandon some standard programming idioms
in the interest of preserving safety. For instance, Cyclone
programmers are required to write region types for functions; the type
inference is only intraprocedural. Ensuring safety in presence of
dynamic regions requires using either unique pointers or
reference-counted objects.  Both approaches are intrusive. For
example, unique pointers constrain, or in some cases forbid, the use
of the familiar iterator pattern, which requires creation of aliases
to objects in a collection. Some standard library functions, for
example, those that use caching, may need to be rewritten.  Moreover,
even with unique pointers, safety cannot be guaranteed statically;
checks against \C{NULL} are needed at run-time to enforce safety. For
ref-counted objects, Cyclone requires programmers to use special
functions (\C{alias\_refptr} and \C{drop\_refptr}) to create and
destroy aliases.  Reference count is affected only by these
functions. An alias going out of scope, for instance, does not
decrement the ref-count. The requirement to use additional constructs
to manage aliases makes reference counting more-or-less as intrusive
as unique pointers.

Our work differs from Cyclone also in terms of its technical
contributions. While Cyclone equips C with a range of region
constructs~\cite{cycloneSCP}, the semantics of (a significant subset
of) such constructs, and the safety guarantees of the language are not
formalized. In contrast, the (static and dynamic) semantics of Broom
has been rigorously defined with respect to a well-understood formal
system (FGJ). The safety guarantees have been formalized and proved.
The core of Broom is very simple; the rules that make up static and
dynamic semantics occupy less than a page each. We believe that the
rigor and simplicity of Broom makes it easy to understand the the
underlying ideas, and apply them in various problem settings. Similar
contrast can be made of region type inference in both the languages.
Cyclone’s type inference was only ever described as being similar to
Tofte and Talpin’s, and it’s effectiveness in presence of tracked
pointers is not clear. In contrast, the complete Ocaml (pseudo) code
of Broom's inference algorithm, was given in the supplement and the
ideas underlying type inference have been described elaborately in the
paper
